{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Wrote a conclusion.

%\begin{figure}[!h]
%\centering
%\begin{tabular}{cc}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
%\end{tabular}
%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
%\label{fig:OTB100_DATASET}
%\end{figure}
%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%----------------------------------------------------------------------

>>>>

%\begin{figure}[!h]
%\centering
%\begin{tabular}{cc}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
%\end{tabular}
%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
%\label{fig:OTB100_DATASET}
%\end{figure}
%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm would be very attractive for any
mobile, unmanned robotic solutions on real-world applications. To make
such applications practical, those algorithms should run faster with
small footprint of computation resouce consumption. To this end, we
proposed an extension of KCF that deploys three KCFs in turn to
address the scale change and dynamic maneuvers of a target. The way we
ran three KCFs in a harmonious way optimal in a sense that efficiently
handled the scale change and effectively learned the translation of
the target. However, by doing so, our algorithm may introduce any
potential drifts. To prevent this from happening, we developed a Bayes
filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. Experimental results showed that the performance of ours are
70.10\% for precision on 20 pixels and 53.00\% for success rate for
OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123.
